ICT-Specific Investment Shocks and Economic Fluctuations \bigskip \\ \normalsize{Evidence and Theory of a General-Purpose Technology}

### 2019-03-07 Latex/Conference_Modena_March2019/Brianti Gati March 2019.tex
presentation almost done

\title{ICT-Specific Investment Shocks and Economic Fluctuations}
%\\ \bigskip \\ \normalsize{Evidence and Theory of a General-Purpose Technology}
\author{Marco Brianti, Boston College\\Laura G\'ati, Boston College}
\institute{Convegno RECent\\Modena}
\date{March 2019}

@@

@@

\frame{\frametitle{Our Contribution}

	\begin{enumerate}
		\item \textbf{Empirical Contribution} that contemporaneous jumps in ICTI explain significant and persistent increases in future TFP
		\begin{itemize}
			\item Structural VAR techniques on U.S. aggregates to identify ICT investment shocks
		\end{itemize}

@@

		\item We analyze a \textbf{theoretical model} to rationalize our empirical findings and draw conclusions concerning the nature of ICT 
		\begin{itemize}
		\item We extend the 2-sector GE model of Greenwood et al. (1997) to accommodate for the role of ICT capital in production
		\end{itemize}
	\end{enumerate}

@@

%\begin{figure}[h!]
%	\subfigure{\includegraphics[width=  0.2]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}} \hspace{.2in} 
%	\subfigure{\includegraphics[width=  0.2]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}} \hspace{.2in} 
%	\subfigure{\includegraphics[width=   0.2]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}} \hspace{.2in} 
%	\subfigure{\includegraphics[width=   0.2]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}} 
%\end{figure}

%\begin{figure}
%	\centering
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}}\qquad
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}}\qquad
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}}\qquad

%		\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}}\qquad
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}}\qquad
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}}\qquad
%\end{figure}

@@

\frame{\frametitle{Variance Decomposition Analysis and Robustness Checks}

	\begin{itemize}
		\item ICT shocks are an \textbf{important driver} of economic fluctuations
	\begin{itemize}
		\item[-] Around $30$\% of TFP fluctuations over 10-year horizon 
		\item[-] Almost $40$\% of GDP fluctuations over BC frequencies
	\end{itemize}

@@

@@

\item \textbf{Results are robust} after
\begin{itemize}
	\item[-] controlling for news shocks \`a la Barsky and Sims
	\item[-] controlling for other shocks estimated via narrative approach
     \item[-] ordering TFP after ICT investment
\end{itemize}

\end{itemize}

@@

\frame{\frametitle{Takeaway}

	We identify a shock specific to the ICT sector where prices and quantities move in different directions

@@

	Altough TFP does not move on impact, it start rising significantly after a couple of years
	\begin{itemize}
		\item this effect is significant and economically meaningful
	\end{itemize}

\begin{itemize}
	\item Supply shocks specific to the ICT sector explain a large part of medium-run TFP fluctuations
	\begin{itemize}
		\item[-] ICT prices fall relatively to CPI
	\end{itemize}
	\item Shocks which explains large part of TFP fluctuations
\end{itemize}

>>>>

\title{ICT-Specific Investment Shocks and Economic Fluctuations \bigskip \\ \normalsize{Evidence and Theory of a General-Purpose Technology}}
\author{Marco Brianti, Boston College\\Laura G\'ati, Boston College}
\institute{Convegno RECent\\Modena}
\date{\textit{March 2019}}

@@

\bigskip

@@

\frame{\frametitle{This Paper}

\bigskip

	\begin{enumerate}
		\item We identify ICT investment shocks using \textbf{SVAR} techniques
		\begin{itemize}
			\item A contemporaneous increase in ICT investment leads to delayed, persistent, and large rise in productivity
             \item Historical decomposition confirms that the doc-com crash explains most of the slowdown in TFP since 2006 
		\end{itemize}

@@

		\item We analyze a \textbf{general equilibrium model} to rationalize our empirical findings 
		\begin{itemize}
		\item Our identified shocks can be interpreted as supply shocks specific to the ICT sector
         \item ICT capital goods boosts productivity of ICT users thorugh a positive externality
\begin{itemize}
\item[$\Rightarrow$] The effectiveness of ICT depends on its own level of diffusion
\end{itemize}
		\end{itemize}
	\end{enumerate}

@@

\bigskip

\begin{columns}[t]
\column{.3\textwidth}
\centering
\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}\\
\bigskip
\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy} 
\column{.3\textwidth}
\centering
\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}\\
\bigskip
\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}
\column{.3\textwidth}
\centering
\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}\\
\bigskip
\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}
\end{columns}

@@

\frame{\frametitle{Related Exercises and Robustness Checks}

\bigskip

	\begin{itemize}
		\item \textbf{Variance Decomposition Analysis}
	\begin{itemize}
		\item[-] Around $30$\% of TFP fluctuations over 10-year horizon 
		\item[-] Almost $40$\% of GDP fluctuations over BC frequencies
	\end{itemize}
\item[$\Rightarrow$]  ICT shocks are an \textbf{important driver} of economic fluctuations

@@

\item \textbf{Historical Decomposition Analysis}
\begin{itemize}
\item[-] Large negative shocks in 2000-2001 (dot-com crash) explain the slowdown in TFP since 2006
\end{itemize}
\item[$\Rightarrow$] ICT shocks \textbf{rationalize} the facts by Fernald et al. (2017)

@@

\item \textbf{Resulness Checks} 
\begin{itemize}
	\item[-] Controlling for news shocks \`a la Barsky and Sims
	\item[-] Controlling for other shocks estimated via narrative approach
\end{itemize}
\item[$\Rightarrow$]  ICT shocks are \textbf{not confounded} with other shocks
\end{itemize}

@@

\frame{\frametitle{Model}

Main objectives of theoretical analysis
\begin{itemize}
\item[1.] Providing structural interpretation to the identified shocks
\begin{itemize}
\item[$\Rightarrow$] ICT shocks move price and quantities in different directions
\end{itemize}
\item[2.] Rationalize the relation between current ICT investment and future TFP
\begin{itemize}
\item[$\Rightarrow$] Why current ICT investment drives future TFP?
\end{itemize}
\end{itemize}

@@

We extend and analyze a 2-sector GE model in the spirit of Greenwood et al. (2007). Two main assumptions are in place,
\begin{itemize}
\item[1.] Second sector specifically produce ICT durable goods to be used as inputs in both sectors' production function
\item[2.] Agents fail to internalize that productivity of both sectors positively depends of the overall ICT diffusion in the economy
\end{itemize}

\frame{\frametitle{Main Equations}

Consumption-good sector
\begin{eqnarray}\label{equation:production_FINAL}
y^c_t(j) = A^c_t \ \big( k^c_{t}(j) \big)^a \ \big( k^i_{t}(j) \big)^b \ \big( l_{t}(j) \big)^{1-a-b}
\end{eqnarray}

ICT-good sector
\begin{eqnarray}\label{equation:productionICT}
y^i_t(q) = A_t^i \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}
\end{eqnarray}

where

\centering
$ A_t^c = \eta_t \ \theta^c_t \ \textcolor{red}{(k^i_{t})^{\gamma}} \ \ \ \text{and} \ \ \ A_t^i = \eta_t \ \theta^i_t \ \textcolor{red}{(k^i_{t})^{\gamma}} $

\frame{\frametitle{Conclusions}

\begin{itemize}
\item Structural VAR analysis unfolds a novel relation between current ICT investment and future TFP
\begin{itemize}
\item[-] Unexpected jumps of ICT investment leads to delayed and persistent rise in productivity
\end{itemize}

\item Theoretical analysis suggests to interpret ICT capital as the general purpose technology of the last three decades
\begin{itemize}
\item[-] ICT diffusions increases the productivity of both ICT users and producers
\end{itemize}

\item The fall in ICT investment during the doc-com crash has the right timing to rationalize the structural break in TFP
\end{itemize}

\frame{\frametitle{Estimated Shocks}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=0.25]{Removing_FLVariables}
		\label{fig:TFP_main}
	\end{center}
\end{figure}
